Sparse model

### 2020-05-03 analysis/sparse_model.Rmd
test mr.ash

$$log(\pi_\theta) \sim U(log(1/M), log(1))$$
$$log(\pi_\beta) \sim U(log(1/J), log(1))$$
We define $h_{SNP}$ and $h_{expr}$ as follows: 
$$
h_{SNP} := \frac{M\sigma_\theta^2}{M\sigma_\theta^2 + Jvar(\tilde{X})\sigma_\beta^2+ 1}$$
$$
h_{expr} := \frac{Jvar(\tilde{X})\sigma_\beta^2}{M\sigma_\theta^2 + Jvar(\tilde{X})\sigma_\beta^2+ 1}$$

>>>>

$$log(\pi_\theta) \sim U(log(1/M), log(1))$$
$$log(\pi_\beta) \sim U(log(1/J), log(1))$$
We define $h_{SNP}$ and $h_{expr}$ as follows: 
$$
h_{SNP} := \frac{\pi_\theta M\sigma_\theta^2}{\pi_\theta M\sigma_\theta^2 + \pi_\beta Jvar(\tilde{X})\sigma_\beta^2+ 1}$$
$$
h_{expr} := \frac{\pi_\beta Jvar(\tilde{X})\sigma_\beta^2}{\pi_\theta M\sigma_\theta^2 + \pi_\beta Jvar(\tilde{X})\sigma_\beta^2+ 1}$$
